Clinical advancement forecasting \thanks{\textit{\underline{Citation}}: \textbf{TBD}}

### 2024-03-29 paper/paper.tex
Fix spelling and grammar errors
Finish refactoring of Figure 2

\begin{figure}[!htb]
  \centering
  \captionsetup{width=.9\linewidth}
  \subfloat[\centering]{\includegraphics[width=.58\textwidth]{relative_risk_mean_across_ta.pdf}}
  \qquad
  \subfloat[\centering]{\includegraphics[width=.36\textwidth]{classifier_metrics_dist_across_ta.pdf}}
  \caption{
    \textbf{Statistical learning optimizes expected target-disease piar advancement rates using longitudinal evidence}.
    (a) Equally-weighted average relative risk estimates across 13 therapeutic areas, by number of top rankings and 3 methods: RDG (ours), RDG-T (ours) and Open Targets composite scores. 
    (b) Receiver operating characteristic (ROC) and average precision scores across the same 13 therapeutic areas with no limit on the number of rankings. 
    See Supplementary~Figure~\ref{fig:relative_risk_by_ta} for raw data underlying (a).
  }
  \label{fig:performance_across_ta}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \captionsetup{width=.9\linewidth}
  \includegraphics[width=1\textwidth]{relative_risk_core_features.pdf}
  \caption{
    \textbf{Performance of individual features and predictive scores as measured by relative risk}.
    RDG model results denoted by \colorbox{Gainsboro}{rdg@N} correspond to results for the \colorbox{Gainsboro}{N} top TD pairs. The same convention is used for \colorbox{Gainsboro}{literature} evidence and the \colorbox{Gainsboro}{time\_\_transition\_\_eq\_X} convention denotes RR estimates when the time since the phase 2 transition is equal to \colorbox{Gainsboro}{X} years. All other features are assessed based on their existence. The counts along the origin indicate how many TD pairs were used to compute the RR numerator.
  }
  \label{fig:relative_risk_core_features}
\end{figure}

@@

>>>>

\begin{figure}[!htb]
  \centering
  \captionsetup{width=.9\linewidth}
  \subfloat[\centering]{\includegraphics[width=.58\textwidth]{relative_risk_mean_across_ta.pdf}}
  \qquad
  \subfloat[\centering]{\includegraphics[width=.36\textwidth]{classifier_metrics_dist_across_ta.pdf}}
  \caption{
    \textbf{Statistical learning optimizes expected target-disease pair advancement rates using longitudinal evidence}.
    (a) Equally-weighted average relative risk estimates across 13 therapeutic areas, by number of top rankings and 3 methods: RDG (ours), RDG-T (ours) and Open Targets composite scores. 
    (b) Receiver operating characteristic (ROC) and average precision scores across the same 13 therapeutic areas with no limit on the number of rankings. 
    See Supplementary~Figure~\ref{fig:relative_risk_by_ta} for raw data underlying (a).
  }
  \label{fig:performance_across_ta}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \captionsetup{width=.9\linewidth}
  \includegraphics[width=1\textwidth]{performance_metric_mean_across_ta.pdf}
  \caption{
    \textbf{Performance of ...}.
  }
  \label{fig:performance_metric_mean_across_ta}
\end{figure}

@@

\begin{figure}
  \centering
  \captionsetup{width=.9\linewidth}
  \includegraphics[width=1\textwidth]{relative_risk_core_features.pdf}
  \caption{
    \textbf{Performance of individual features and predictive scores as measured by relative risk}.
    RDG model results denoted by \colorbox{Gainsboro}{rdg@N} correspond to results for the \colorbox{Gainsboro}{N} top TD pairs. The same convention is used for \colorbox{Gainsboro}{literature} evidence and the \colorbox{Gainsboro}{time\_\_transition\_\_eq\_X} convention denotes RR estimates when the time since the phase 2 transition is equal to \colorbox{Gainsboro}{X} years. All other features are assessed based on their existence. The counts along the origin indicate how many TD pairs were used to compute the RR numerator.
  }
  \label{fig:relative_risk_core_features}
\end{figure}
